---
title: "Using envDocument"
author: "Donald Jackson (donald.jackson@bms.com)"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The `envDocument` package provides a function `env_doc()` which collects information about the environment in which an analysis is run.  Currently, this includes:

+ R version
+ Attached packages with version and repository
+ General system information including OS and user
+ Script information including working diretory. script path and modification time
+ Git commit information for script including tracking status, commit status, and remote

The primary purpose is to capture information for inclusion in an analysis report.  As such, the call to env_doc() should be made after all analyses are run.



Some functions, especialy `get_scriptPath()` and `getRepo()`, may be useful in ohter settings.

# Examples

```{r}
library(envDocument) 
library(knitr)


kable(env_doc()) # with git2r installed
# kable(env_doc(git = FALSE)) # without git2r
```

New option in v2.2: option "table" pretty-prints each section separately.
Requires `knitr`.  Specify `results = "asis"` in knitr chunk options to make sure
table is formatted in markdown (no leading ##).

```{r table, results = "asis"}
# env_doc("table")
```

End of test
